DraftFunctions

### 2021-12-31 R/DraftFunctions.Rmd
Parallelization and iterations summary function #48
Renaming

@@

```{r SpeciesCriteria table code}
SpeciesCriteria <- read_csv("D:/VSC Kourou/DATA/SpeciesCriteria.csv",
                            col_types = cols(Commercial = col_factor(levels = c("0",
                                                                                "1", "2")), MinFD = col_number(),
                                             UpMinFD = col_number(), MaxFD = col_number()),
                            locale = locale(encoding = "Latin1")) %>%
  separate(ScientificName, sep = " ", into = c("Genus", "Species"), remove = T) %>% 
  mutate(Aggregative = ifelse(VernName == "Angélique" | VernName == "Gonfolo rose",
                              TRUE, FALSE))
# unite(Genus, Species, col = "ScientificName", sep = "_", remove = F)

SpeciesCriteria$VernName <- tolower(SpeciesCriteria$VernName)

>>>>

# LoggingSimulationOutputs <- Rslt
# usethis::use_data(LoggingSimulationOutputs)

@@

```{r SpeciesCriteria table code}
SpeciesCriteria <- read_csv("D:/VSC Kourou/DATA/SpeciesCriteria.csv",
                            col_types = cols(Commercial = col_factor(levels = c("0",
                                                                                "1", "2")), MinFD = col_number(),
                                             UpMinFD = col_number(), MaxFD = col_number()),
                            locale = locale(encoding = "Latin1")) %>%
  separate(ScientificName, sep = " ", into = c("Genus", "Species"), remove = T) %>% 
  mutate(Aggregative = ifelse(CommercialName == "Angélique" | CommercialName == "Gonfolo rose",
                              TRUE, FALSE))
# unite(Genus, Species, col = "ScientificName", sep = "_", remove = F)

SpeciesCriteria$CommercialName <- tolower(SpeciesCriteria$CommercialName)
